Evaluation

### 2018-11-06 evaluation.Rmd

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
species_names = portalr::FullPath('PortalData/Rodents/Portal_rodent_species.csv', '~') %>%
  read.csv(stringsAsFactors=FALSE, na.strings = '') %>%
  select(species = speciescode, full_species_name = scientificname)

@@

new_moon_file = portalr::FullPath('PortalData/Rodents/moon_dates.csv', '~')
new_moons = read.csv(new_moon_file)
new_moons$censusdate = as.Date(new_moons$censusdate)

>>>>

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
species_names = portalr:::full_path('PortalData/Rodents/Portal_rodent_species.csv', '~') %>%
  read.csv(stringsAsFactors=FALSE, na.strings = '') %>%
  select(species = speciescode, full_species_name = scientificname)

@@

new_moon_file = portalr:::full_path('PortalData/Rodents/moon_dates.csv', '~')
new_moons = read.csv(new_moon_file)
new_moons$censusdate = as.Date(new_moons$censusdate)
